Analyzing the impact of social attributes on commit integration success

### 2017-02-21 Paper/MSRChallenge2017.tex
a bit of space in the intro
space saving

\usepackage[usenames,dvipsnames]{color}
%\newcommand{\todo}[1]
%  {{\scriptsize \textbf{\color{red} {#1}}}}
\newcommand{\todo}[1] {}
\newcommand{\clg}[1]
  {{\scriptsize \textbf{\color{blue} {CLG says: #1}}}}

@@

\paragraph{Goal}
The goal of this study is to identify and understand the relationship 
between the social factors that describe the
developer's experience (stars, followers, etc.) and technical properties that
describe the commit's complexity
(files added, files modified, etc.)
when predicting the likelihood a developer's commit
to be considered successfully integrated in the project. We define successful
integration as passing the continuous integration build tests in the project.

\paragraph{Question}
Previous studies have identified a relationship between technical and social 
factors and pull request acceptance. We are interested in understanding if
social factors, used as a proxy for experience, can be used to predict
a different success measure: commit integration success, therefore giving
developers and integrators another tool to be able to identify the quality
of a contribution performed by a particular developer.

Therefore our main research question is presented as follows:

@@

Depending on the results of this question, we can further explore which
attributes are most important for predicting build integration success.

@@

\paragraph{Metric}
We measure quality software contributions by based on the build status of the
commit: if the build passes or fails.
To determine which factors are important for predicting build success, we used
a decision tree classifier~\cite{Quinlan86}, because decision tress are well a 
tested supervised classifier that are easy to interpret.
To explore the question of technical and social factors, we first build a
decision tree classifier using only the technical factors.  This first model
allowed us to understand how well commit complexity estimated build integration
success.  We then added the social factors to understand how the social factors
integrated with the technical factors when predicting build integration success.
We evaluated the predictive power of these two 
models with 10-fold cross validation.
\section{Building Dataset}
\label{approach}

@@

We scraped the commit author's
\textit{username} from a commit page. If the scraper was able to find the username, the
scraper went to the user's profile information
(\textit{https://github.com/\textbf{UserName}}).

The scraper then extracted the following items from the user's
profile.

>>>>

\usepackage[usenames,dvipsnames]{color}
\newcommand{\todo}[1]
  {{\scriptsize \textbf{\color{red} {#1}}}}
%\newcommand{\todo}[1] {}
\newcommand{\clg}[1]
  {{\scriptsize \textbf{\color{blue} {CLG says: #1}}}}

@@

\vspace{1ex}
\noindent\textbf{Goal.}
The goal of this study is to identify and understand the relationship 
between the social factors that describe the
developer's experience (stars, followers, etc.) and technical properties that
describe the commit's complexity
(files added, files modified, etc.)
when predicting the likelihood a developer's commit
to be considered successfully integrated in the project. We define successful
integration as passing the continuous integration build tests in the project.

\vspace{1ex}

\noindent\textbf{Question.}
Previous studies have identified a relationship between technical and social 
factors and pull request acceptance. We are interested in understanding if
social factors, used as a proxy for experience, can be used to predict
a different success measure: commit integration success, therefore giving
developers and integrators another tool to be able to identify the quality
of a contribution performed by a particular developer.
%
Therefore our main research question, upon which we can build by investigating particular attributes, is:

@@

@@

\vspace{1ex}
\noindent\textbf{Metric.} We measure quality software contributions by based on the build status of the
commit: if the build passes or fails.
To determine which factors are important for predicting build success, we used
a decision tree classifier~\cite{Quinlan86}, because decision tress are well a 
tested supervised classifier that are easy to interpret.
To explore the question of technical and social factors, we first build a
decision tree classifier using only the technical factors.  This first model
allowed us to understand how well commit complexity estimated build integration
success.  We then added the social factors to understand how the social factors
integrated with the technical factors when predicting build integration success.
We evaluated the predictive power of these two 
models with 10-fold cross validation.

\section{Building Dataset}
\label{approach}

@@

We scraped the commit author's
\textit{username} from each commit page, and then
collected user's public profile information. 
%(\textit{https://github.com/\textbf{UserName}}). 
%
The scraper then extracted the following items from the user's
profile.
